---
title: "score_forecasts"
author: "Li Shandross"
date: "3/25/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("thief")
library(forecast)
library(lubridate)
library(tidyverse)
library(zoltr)
library(covidHubUtils)
```

## Load in truth data and forecasts
We load in the hospitalization truth data and our forecasts. (Note: The load forecast parentheses function wasn't working, so alternate code is written to achieve the same output.)   
```{r, message=FALSE, fig.width=12, fig.height=8}
full_hosp_truth <- load_truth("HealthData", 
                         "inc hosp", 
                         temporal_resolution="daily",
                         data_location = "remote_hub_repo")

inc_hosp_targets <- paste(0:35, "day ahead inc hosp")

load("../data/loadedfc_scores.RData")


# models <- c("Base_arima_noTrans", "Multiple3_arima_noTrans", "Topmost8_arima_noTrans")
# file_paths <- list(list.files(path = "../data/Base_arima_noTrans/", pattern=".csv", full.names=TRUE),
#   list.files(path = "../data/covidTHieF-Multiple3_arima_noTrans/", pattern=".csv", full.names=TRUE),
#   list.files(path = "../data/Topmost8_arima_noTrans/", pattern=".csv", full.names=TRUE))
# 
# forecasts <- read_csv(file_paths[[1]][1]) %>% mutate(model=models[1])
# for (i in 1:3) {
#   for (j in 1:31) {
#     if(i + j != 2) {
#       df <- read_csv(file_paths[[i]][j]) %>%
#         mutate(model = models[i])
#       forecasts <- rbind(forecasts, df)
#     }
#   }
# }
# 
# forecasts2 <-
#   forecasts %>%
#     separate(target,
#       into=c("horizon", "temp"),
#       sep=" "
#     ) %>%
#     mutate(
#       horizon=as.numeric(horizon), 
#       temporal_resolution="day",
#       target_variable="inc hosp"
#     ) %>%
#     select(model, forecast_date, location, horizon, temporal_resolution, target_variable, target_end_date:value) %>%
#     left_join(hub_locations, by=c("location"="fips"))
```

## Plot Forecasts
We plot forecasts for three locations (Us National, Texas, and Vermont) for each of the three models. The two state locations were chosen as the highest and lowest hospitalization count locations. The plotted forecasts are spaced 4 weeks apart with 1 - 28 day ahead horizons, starting with the first forecast date, 12/07/20, until the end of the training period, 07/05/21.   

```{r, warning=FALSE, message=FALSE}
locs <- full_hosp_truth %>%
  filter(target_end_date <= as.Date("2021-07-05")) %>%
  group_by(location) %>%
  summarize(cum_value=sum(value)) %>%
  ungroup() %>%
  arrange(desc(cum_value)) %>%
  filter(row_number() %in% c(1, 2, 53)) %>%
  pull(location)

fc_dates <- c(as.Date("2020-12-07") + weeks(4*(0:7)))

for (i in 1:3) {
  fdat <-forecasts2 %>% filter(location == locs[i], forecast_date %in% fc_dates)
  
  p <- plot_forecasts(fdat, 
                      target_variable = "inc hosp", 
                      intervals = c(.5, .95), 
                      truth_source = "HealthData",
                      use_median_as_point = TRUE,
                      facet = model ~.,
                      facet_nrow = 3,
                      facet_scales = "free_y",
                      fill_by_model = TRUE, 
                      plot=FALSE)

  pt <- p +
    scale_x_date(name=NULL, limits=c(as.Date("2020-10-01"), as.Date("2021-07-05")), 
              date_breaks = "2 months", date_labels = "%b") +
    theme(axis.ticks.length.x = unit(0.5, "cm"),
          axis.text.x = element_text(vjust = 7, hjust = -0.2))
          
  print(pt)
}
```

The plots don't show much visible difference between the three models (although this is partially due to the fact that the yscales are free and are not consistent even for the same location). However, it is clear that performance differs by location, all three models performing the worst for Texas and most closely following the trend line for the US National truth. We investigate model accuracy more deeply by scoring the forecasts for each model and calculating appropriate metrics.   

## Score forecasts
We calculate metrics for all three models, aggregating by horizon. Since hospitalizations are forecasted at a daily time scale, a new horizon week variable is created in which scoring metrics are averaged over from a single week Tuesday to the following Monday. We perform these calculations for the entire training phase as well as for each of the two waves that occurred during the training phase.   

```{r}
# scores <- score_forecasts(forecasts=forecasts2, return_format="wide", truth=full_hosp_truth, use_median_as_point=TRUE)
#getwd()
# save(forecasts2, scores, file="../data/loadedfc_scores.RData")
```

### Overall metrics
```{r}
# US National
overall_metrics_US <- scores %>%
  filter(horizon <= 28, 
         target_end_date <= as.Date("2021-07-05"),
         location == "US") %>%
  mutate(
    horizon_wk = case_when(
      horizon %in% c(1:7) ~ 1,
      horizon %in% c(8:14) ~ 2,
      horizon %in% c(15:21) ~ 3,
      horizon %in% c(22:28) ~ 4
    )
  ) %>%
  group_by(model, horizon_wk) %>%
  summarize(
    wis = mean(wis), mae=mean(abs_error),
    coverage_50 = mean(coverage_50),
    coverage_95 = mean(coverage_95)
  )
knitr::kable(overall_metrics_US)

# Aggregated for all states and territories
overall_metrics_states <- scores %>%
  filter(horizon <= 28, 
         target_end_date <= as.Date("2021-07-05"),
         location != "US") %>%
  mutate(
    horizon_wk = case_when(
      horizon %in% c(1:7) ~ 1,
      horizon %in% c(8:14) ~ 2,
      horizon %in% c(15:21) ~ 3,
      horizon %in% c(22:28) ~ 4
    )
  ) %>%
  group_by(model, horizon_wk) %>%
  summarize(
    wis = mean(wis), mae=mean(abs_error),
    coverage_50 = mean(coverage_50),
    coverage_95 = mean(coverage_95)
  )
knitr::kable(overall_metrics_states)
```

When splitting the results so that US National is separate, we find that for US National the Base_arima_noTrans model performed the best both in terms of WIS and MAE as well as PI Coverage, followed by the Topmost8_arima_noTrans model and finally the Multiple3_arima_noTrans model, with a noticeable difference in performance between models. On the other hand, for states we find that the Topmost8_arima_noTrans model performed the best, followed closely by the Multiple3_arima_noTrans model (which actually had slightly better 50% PI Coverage), and then much further behind the Base_arima_noTrans model. There was noticeably better PI coverage for the US National forecasts, but we cannot say much about the WIS and MAE since these metrics are scale-dependent and we are holding off on comparing to the baseline until the testing phase.

### Metrics by wave
```{r}  
# US National
wave_metrics_US <- scores %>%
  filter(horizon <= 28, 
         target_end_date <= as.Date("2021-07-05"),
         location == "US") %>%
  mutate(
    horizon_wk = case_when(
      horizon %in% c(1:7) ~ 1,
      horizon %in% c(8:14) ~ 2,
      horizon %in% c(15:21) ~ 3,
      horizon %in% c(22:28) ~ 4
    ),
    wave = case_when(
      forecast_date <= as.Date("2021-03-17") ~"winter21",
      forecast_date >= as.Date("2021-03-17") ~"alpha"
    )
  ) %>%
  group_by(wave, model, horizon_wk) %>%
  summarize(
    wis = mean(wis), mae=mean(abs_error),
    coverage_50 = mean(coverage_50),
    coverage_95 = mean(coverage_95)
  )
  
knitr::kable(wave_metrics_US)

# Aggregated for all states and territories
wave_metrics_states <- scores %>%
  filter(horizon <= 28, 
         target_end_date <= as.Date("2021-07-05"),
         location != "US") %>%
  mutate(
    horizon_wk = case_when(
      horizon %in% c(1:7) ~ 1,
      horizon %in% c(8:14) ~ 2,
      horizon %in% c(15:21) ~ 3,
      horizon %in% c(22:28) ~ 4
    ),
    wave = case_when(
      forecast_date <= as.Date("2021-03-17") ~"winter21",
      forecast_date >= as.Date("2021-03-17") ~"alpha"
    )
  ) %>%
  group_by(wave, model, horizon_wk) %>%
  summarize(
    wis = mean(wis), mae=mean(abs_error),
    coverage_50 = mean(coverage_50),
    coverage_95 = mean(coverage_95)
  )
  
knitr::kable(wave_metrics_states)
```

Based on the above metrics, we can see that generally the Topmost8_arima_noTrans model performed the best both in terms of WIS and MAE as well as PI Coverage, whereas the Multiple3_arima_noTrans model performed next best for PI Coverage but the Base_arima_noTrans model performed second best for WIS and MAE. There is not much difference between the metrics calculated for the entire training phase versus those split by wave, although notably the models perform better during the longer winter21 wave compared to the shorter alpha wave. The PI coverage is not great for any of the models, although it is slightly better for the 95% interval compared to the 50% one.

For US National during the alpha wave, the Base_arima_noTrans model performed the best for every metric and every horizon, followed by the Topmost8_arima_noTrans model, both of which were noticeably better than the Multiple3_arima_noTrans model for all metrics and horizons. However, during the winter21 wave the Multiple3_arima_noTrans model out performed the other two models at longer horizons for all metrics except 3 week ahead 50% PI coverage where the Base_arima_noTrans performed best. At shorter horizons, though, the Base_arima_noTrans tended to perform best for all metrics, except for one week ahead 50% of PI Coverage in which the Topmost8_arima_noTrans model did the best. During the alpha wave, the best models had noticeably good coverage rates, very close to the nominal levels. The results from the alpha wave in terms of model ranking seem to match those of the overall results for the US National level.   

For states during the alpha wave, the Topmost8_arima_noTrans model performed the best for every metric and every horizon, followed by the Multiple3_arima_noTrans model, both of which were better than the Base_arima_noTrans model for all (noticeably so for most) metrics and horizons. However, during the winter21 wave the Multiple3_arima_noTrans model out performed the other two models for all metrics except 95% PI coverage where the Base_arima_noTrans performed best, although not by much. Unsurprisingly, the Topmost8_arima_noTrans performed next best for most metrics, followed by the Base_arima_noTrans model. During the Winter21 wave, all the models had noticeably better performance for all metrics compared to the alpha wave, opposite of that for the wave breakdown of the US National level. However, the results from the alpha wave in terms of model ranking seem to match those of the overall results for the states.   
