---
title: "score_forecasts"
author: "Li Shandross"
date: "3/25/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("thief")
library(forecast)
library(lubridate)
library(tidyverse)
library(zoltr)
library(covidHubUtils)
```

## Load in truth data and forecasts
We load in the hospitalization truth data and our forecasts. (Note: The load forecast parentheses function wasn't working, so alternate code is written to achieve the same output.)   
```{r, message=FALSE, fig.width=12, fig.height=8}
full_hosp_truth <- load_truth("HealthData", 
                         "inc hosp", 
                         temporal_resolution="daily",
                         data_location = "remote_hub_repo")

inc_hosp_targets <- paste(0:35, "day ahead inc hosp")

load("../data/loadedfc_scores.RData")


# models <- c("Base_arima_noTrans", "Multiple3_arima_noTrans", "Topmost8_arima_noTrans")
# file_paths <- list(list.files(path = "../data/Base_arima_noTrans/", pattern=".csv", full.names=TRUE),
#   list.files(path = "../data/covidTHieF-Multiple3_arima_noTrans/", pattern=".csv", full.names=TRUE),
#   list.files(path = "../data/Topmost8_arima_noTrans/", pattern=".csv", full.names=TRUE))
# 
# forecasts <- read_csv(file_paths[[1]][1]) %>% mutate(model=models[1])
# for (i in 1:3) {
#   for (j in 1:31) {
#     if(i + j != 2) {
#       df <- read_csv(file_paths[[i]][j]) %>%
#         mutate(model = models[i])
#       forecasts <- rbind(forecasts, df)
#     }
#   }
# }
# 
# forecasts2 <-
#   forecasts %>%
#     separate(target,
#       into=c("horizon", "temp"),
#       sep=" "
#     ) %>%
#     mutate(
#       horizon=as.numeric(horizon), 
#       temporal_resolution="day",
#       target_variable="inc hosp"
#     ) %>%
#     select(model, forecast_date, location, horizon, temporal_resolution, target_variable, target_end_date:value) %>%
#     left_join(hub_locations, by=c("location"="fips"))
```

## Plot Forecasts
We plot forecasts for three locations (Us National, Texas, and Vermont) for each of the three models. The two state locations were chosen as the highest and lowest hospitalization count locations. The plotted forecasts are spaced 4 weeks apart with 1 - 28 day ahead horizons, starting with the first forecast date, 12/07/20, until the end of the training period, 07/05/21.   

```{r, warning=FALSE, message=FALSE}
locs <- full_hosp_truth %>%
  filter(target_end_date <= as.Date("2021-07-05")) %>%
  group_by(location) %>%
  summarize(cum_value=sum(value)) %>%
  ungroup() %>%
  arrange(desc(cum_value)) %>%
  filter(row_number() %in% c(1, 2, 53)) %>%
  pull(location)

fc_dates <- c(as.Date("2020-12-07") + weeks(4*(0:7)))

for (i in 1:3) {
  fdat <-forecasts2 %>% filter(location == locs[i], forecast_date %in% fc_dates)
  
  p <- plot_forecasts(fdat, 
                      target_variable = "inc hosp", 
                      intervals = c(.5, .95), 
                      truth_source = "HealthData",
                      use_median_as_point = TRUE,
                      facet = model ~.,
                      facet_nrow = 3,
                      facet_scales = "free_y",
                      fill_by_model = TRUE, 
                      plot=FALSE)

  pt <- p +
    scale_x_date(name=NULL, limits=c(as.Date("2020-10-01"), as.Date("2021-07-05")), 
              date_breaks = "2 months", date_labels = "%b") +
    theme(axis.ticks.length.x = unit(0.5, "cm"),
          axis.text.x = element_text(vjust = 7, hjust = -0.2))
          
  print(pt)
}
```

The plots don't show much visible difference between the three models (although this is partially due to the fact that the yscales are free and are not consistent even for the same location). However, it is clear that performance differs by location, all three models performing the worst for Texas and most closely following the trend line for the US National truth. We investigate model accuracy more deeply by scoring the forecasts for each model and calculating appropriate metrics.   

## Score forecasts
We calculate metrics for all three models, aggregating by horizon. Since hospitalizations are forecasted at a daily time scale, a new horizon week variable is created in which scoring metrics are averaged over from a single week Tuesday to the following Monday. We perform these calculations for the entire training phase as well as for each of the two waves that occurred during the training phase.   

```{r}
# scores <- score_forecasts(forecasts=forecasts2, return_format="wide", truth=full_hosp_truth, use_median_as_point=TRUE)
#getwd()
# save(forecasts2, scores, file="../data/loadedfc_scores.RData")


# Overall metrics
overall_metrics <- scores %>%
  filter(horizon <= 28, target_end_date <= as.Date("2021-07-05")) %>%
  mutate(
    horizon_wk = case_when(
      horizon %in% c(1:7) ~ 1,
      horizon %in% c(8:14) ~ 2,
      horizon %in% c(15:21) ~ 3,
      horizon %in% c(22:28) ~ 4
    )
  ) %>%
  group_by(model, horizon_wk) %>%
  summarize(
    wis = mean(wis), mae=mean(abs_error),
    coverage_50 = mean(coverage_50),
    coverage_95 = mean(coverage_95)
  )
knitr::kable(overall_metrics)
  
# Metrics by wave
wave_metrics <- scores %>%
  filter(horizon <= 28, target_end_date <= as.Date("2021-07-05")) %>%
  mutate(
    horizon_wk = case_when(
      horizon %in% c(1:7) ~ 1,
      horizon %in% c(8:14) ~ 2,
      horizon %in% c(15:21) ~ 3,
      horizon %in% c(22:28) ~ 4
    ),
    wave = case_when(
      forecast_date <= as.Date("2021-03-17") ~"winter21",
      forecast_date >= as.Date("2021-03-17") ~"alpha"
    )
  ) %>%
  group_by(model, wave, horizon_wk) %>%
  summarize(
    wis = mean(wis), mae=mean(abs_error),
    coverage_50 = mean(coverage_50),
    coverage_95 = mean(coverage_95)
  )
  
knitr::kable(wave_metrics)
```

Based on the above metrics, we can see that generally the Topmost8_arima_noTrans model performed the best both in terms of WIS and MAE as well as PI Coverage, whereas the Multiple3_arima_noTrans model performed next best for PI Coverage but the Base_arima_noTrans model performed second best for WIS and MAE. There is not much difference between the metrics calculated for the entire training phase versus those split by wave, although notably the models perform better during the longer winter21 wave compared to the shorter alpha wave. The PI coverage is not great for any of the models, although it is slightly better for the 95% interval compared to the 50% one.

